\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-21 notes/2loopNLSM.tex
Added actual numbers into YM discussion.

@@

First, we analyze the power-counting assumption.  In our labeling of
the two loop Jacobi-basis diagrams, shown in \ace{Figure out fig}, we
find that the power counting bound proposed by Bern, Davies, and Nohle
leads to an initial ansatz with XX terms in the double-box, and YY
terms for the penta-triangle.  However, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?} demonstrates that constructing Feynman rules that
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  We therefore attempt to find an
off-shell color-dual Yang--Mills representation in which all power
counting restrictions are lifted.

Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an initial ansatz with 10,010 terms each.
Imposing diagram automorphisms on the two basis diagrams, we reduce
the number of terms to XX.  Gauge invariance on support of the maximal
cuts of the basis diagrams further reduces the remaining freedom to
YY.  The power-counting restriction of BDN would reduce this count to
ZZ.  In the original BDN work, they imposed three spanning generalized
unitarity cuts, shown in [].  Instead of directly imposing the
spanning cuts, we proceed with the relaxed version of the method of
maximal cuts used above in the pion construction [\ace{is James going
  to talk about something along this line in the pions section?}].  We
find that even with the completely generic ansatz, the representation
fails to satisfy the next-to-next-to-maximal cut shown in [].
Notably, imposing the BDN power-counting constraints additionally
causes a discrepancy with the N$^2$-max cuts show in [].

>>>>

\usepackage{showkeys}

@@

First, we analyze the power-counting assumption.  In our labeling of
the two loop Jacobi-basis diagrams, shown in \ace{Figure out fig}, we
find that the power counting bound proposed by Bern, Davies, and Nohle
leads to an initial ansatz with 10,000 terms in the double-box, and 9,849
terms for the penta-triangle.  However, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?} demonstrates that constructing Feynman rules that
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  We therefore attempt to find an
off-shell color-dual Yang--Mills representation in which all power
counting restrictions are lifted.

Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an initial ansatz with 10,010 terms each.
Imposing both diagram automorphisms and maximal-cut gauge invariance
on both of the basis diagrams reduces the ansatz to 2,235 terms in the
double-box and 4,133 terms in the penta-triangle.  The power-counting
restriction of BDN would reduce the counts to 2232 and 4072,
respectively.  In the original BDN work, they imposed three spanning
generalized unitarity cuts, shown in [].  Instead of directly imposing
the spanning cuts, we proceed with a relaxed version of the method of
maximal cuts [] in order to more-directly identify the location of
tension between kinematic Jacobi relations and unitarity constraints.
We find that even with the completely generic ansatz,
the representation fails to satisfy the next-to-next-to-maximal cut
shown in [].  Notably, imposing the BDN power-counting constraints
additionally causes a discrepancy with the N$^2$-max cuts show in [].
